VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_eval.tex

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing a data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally based 
on~\cite{extreme_binning09}.
\subsection{Settings}
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machine nodes failed in a cluster with $p=100$ physical machines.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and thus calculate the average availability of VM snapshots.
The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. With different $p$ values, how the availability varies when 
the number of failures in the cluster changes.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
settings
and
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
duplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%.
When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
more index space is allocated  per machine for  PDS fingerprint lookup.
% increases from 100MB to 200MB per physical machine as discussed later. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

{\bf Processing Time breakdown without I/O throttling}.
Table~\ref{tab:vc_srb_combined} shows
the  average  processing  time of  a dirty VM segment in milliseconds
under VC and Stateless Routing with Binning (SRB). 
VC uses $\sigma=2\%$ and $4\%$.
The overall processing latency of SRB is about 23.9\% slower than VC.
For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time. 
It has a breakdown of processing time.
``Read/Write'' includes snapshot reading and writing from disk, and 
updating of the metadata.
``Network'' includes the cost of transferring raw and meta data from one machine to another during 
snapshot read and write.
``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
This includes PDS data lookup for VC and index lookup from disk in SRB. 
The network transfer time for VC and SRB is about the same, because the 
amount of raw data they transfer is comparable.
SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
 while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
SRB also has a higher cost for index access and fingerprint comparison because most chunk fingerprints are routed
to remote machines for comparison while   VC handles most chunk fingerprints locally.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when when I/O throttling is not applied to control the usage.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
after compression.  The underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46GB/second 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset, each version of total snapshots  has abut  1TB per machine for 25 VMs and  thus  each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

>>>>

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally based 
on~\cite{extreme_binning09}.
\subsection{Settings}
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machines failed in a cluster with $p=100$ physical machines.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and thus calculate the average availability of VM snapshots.
The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. With different $p$ values, how the availability varies when 
the number of failures in the cluster changes.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%.
When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
more index space is allocated  per machine for  PDS fingerprint lookup.
% increases from 100MB to 200MB per physical machine as discussed later. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

{\bf Processing Time breakdown without I/O throttling}.
Table~\ref{tab:vc_srb_combined} shows

the  average  time breakdown for processing a dirty VM segment in milliseconds
under VC and Stateless Routing with Binning (SRB). 
VC uses $\sigma=2\%$ and $4\%$.
The overall processing latency of SRB is about 23.9\% slower than VC.
For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time. 
It has a breakdown of processing time.
``Read/Write'' includes snapshot reading and writing from disk, and 
updating of the metadata.
``Network'' includes the cost of transferring raw and meta data from one machine to another during 
snapshot read and write.
``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
This includes PDS data lookup for VC and index lookup from disk in SRB. 
The network transfer time for VC and SRB is about the same, because the 
amount of raw data they transfer is comparable.
SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
 while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
SRB also has a higher cost for index access and fingerprint comparison because most chunk fingerprints are routed
to remote machines for comparison while   VC handles most chunk fingerprints locally.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of the software layer
when when I/O throttling is not applied to control usage. The
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
``QFS'' is the write request traffic to the underlying file system after compression.
For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
after compression.  The underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46GB/second 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset, each version of total snapshots  has abut  1TB per machine for 25 VMs and  thus  each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.
